---
title: "Correlations"
date: “2022-03-17"
output:
  workflowr::wflow_html:
    toc: FALSE
    self_contained: no
    df_print: tibble
    theme: spacelab
    code_folding: show
editor_options:
  chunk_output_type: console

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Correlation Plots
The results of the univariate and multivariate analysis methods did not show a significant improvement in the multivariate method. The next step of this project is to determine if there is a correlation between the phenotypes. If there is no correlation, then it makes sense that the multivariate analysis did not yield better results than univariate analysis. If there is correlation then the data needs to be reanalyzed. 
Below are the plots for the correlation for every phenotypic comparison. On the x-axis the labels give the two categories of phenotypes being analyzed. For example female_18_female_25 is the correlation between the lifespan for a female in the 18oC environment and the lifespan for a female in the 25oC environment. The y-axis is the correlation value on a 0-1 scale. 

## Female Correlation Plot
```{r}
library(ggplot2)

###Reading in results
rg_res_female <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_rg_female.rds")

###Objects for the rg data
female_18_female_25 = as.data.frame(rg_res_female$female_18_female_25)
colnames(female_18_female_25) = "female_18_female_25"
female_18_female_28 = as.data.frame(rg_res_female$female_18_female_28)
colnames(female_18_female_28) = "female_18_female_28"
female_25_female_28 = as.data.frame(rg_res_female$female_25_female_28)
colnames(female_25_female_28) = "female_25_female_28"

###COMBINE AND STACK
female_rg <- cbind(female_18_female_25,
                female_18_female_28,
                female_25_female_28)

female_rg <- stack(female_rg)

###Make Female Boxplot
boxplot_female <- ggplot(female_rg, aes(x=ind, y=values))+
  geom_boxplot()+
  labs(title = 'Female Correlation Plot', x = 'Temperature Groups', y = 'Correlation Values')+
  scale_y_continuous(limits=c(0,1))
boxplot_female
```


## Male Correlation Plot
```{r}
library(ggplot2)

###Reading in results
rg_res_male <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_rg_male.rds")

###Objects for the rg data
male_18_male_25 = as.data.frame(rg_res_male$male_18_male_25)
colnames(male_18_male_25) = "male_18_male_25"
male_18_male_28 = as.data.frame(rg_res_male$male_18_male_28)
colnames(male_18_male_28) = "male_18_male_28"
male_25_male_28 = as.data.frame(rg_res_male$male_25_male_28)
colnames(male_25_male_28) = "male_25_male_28"

male_rg <- cbind(male_18_male_25,
                male_18_male_28,
                male_25_male_28)

male_rg <- stack(male_rg)

###Make All Boxplot
boxplot_male <- ggplot(male_rg, aes(x=ind, y=values))+
  geom_boxplot()+
  labs(title = 'Male Correlation Plot', x = 'Temperature Groups', y = 'Correlation Values')+
  scale_y_continuous(limits=c(0,1))
boxplot_male
```

## 18C Correlation Plot
```{r}
library(ggplot2)

###Reading in results
rg_res_18c <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_rg_18c.rds")

###Objects for the rg data
female_18_male_18 = as.data.frame(rg_res_18c$female_18_male_18)
colnames(female_18_male_18) = "female_18_male_18"

temp18c_rg <- cbind(female_18_male_18)

temp18c_rg <- stack(temp18c_rg)

###Make All Boxplot
boxplot_18c <- ggplot(temp18c_rg, aes(x=ind, y=values))+
  geom_boxplot()+
  labs(title = '18C Correlation Plot', x = 'Sex Groups', y = 'Correlation Values')+
  scale_y_continuous(limits=c(0,1))
boxplot_18c
```

## 25C Correlation Plot
```{r}
library(ggplot2)

###Reading in results
rg_res_25c <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_rg_25c.rds")

###Objects for the rg data
female_25_male_25 = as.data.frame(rg_res_25c$female_25_male_25)
colnames(female_25_male_25) = "female_25_male_25"

temp25c_rg <- cbind(female_25_male_25)

temp25c_rg <- stack(temp25c_rg)

###Make All Boxplot
boxplot_25c <- ggplot(temp25c_rg, aes(x=ind, y=values))+
  geom_boxplot()+
  labs(title = '25C Correlation Plot', x = 'Sex Groups', y = 'Correlation Values')+
  scale_y_continuous(limits=c(0,1))
boxplot_25c
```

## 28C Plot
```{r}
library(ggplot2)

###Reading in results
rg_res_28c <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_rg_28c.rds")

###Objects for the rg data
female_28_male_28 = as.data.frame(rg_res_28c$female_28_male_28)
colnames(female_28_male_28) = "female_28_male_28"

temp28c_rg <- cbind(female_28_male_28)

temp28c_rg <- stack(temp28c_rg)

###Make All Boxplot
boxplot_28c <- ggplot(temp28c_rg, aes(x=ind, y=values))+
  geom_boxplot()+
  labs(title = '28C Correlation Plot', x = 'Sex Groups', y = 'Correlation Values')+
  scale_y_continuous(limits=c(0,1))
boxplot_28c
```

## All Correlation Plots
```{r}
library(ggplot2)

###Reading in results
rg_res <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_rg.rds")

###Objects for the rg data
female_18_female_25 = as.data.frame(rg_res$female_18_female_25)
  colnames(female_18_female_25) = "female_18_female_25"
female_18_female_28 = as.data.frame(rg_res$female_18_female_28)
  colnames(female_18_female_28) = "female_18_female_28"
female_18_male_18 = as.data.frame(rg_res$female_18_male_18)
  colnames(female_18_male_18) = "female_18_male_18"
female_18_male_25 = as.data.frame(rg_res$female_18_male_25)
  colnames(female_18_male_25) = "female_18_male_25"
female_18_male_28 = as.data.frame(rg_res$female_18_male_28)
  colnames(female_18_male_28) = "female_18_male_28"
female_25_female_28 = as.data.frame(rg_res$female_25_female_28)
  colnames(female_25_female_28) = "female_25_female_28"
female_25_male_18 = as.data.frame(rg_res$female_25_male_18)
  colnames(female_25_male_18) = "female_25_male_18"
female_25_male_25 = as.data.frame(rg_res$female_25_male_25)
  colnames(female_25_male_25) = "female_25_male_25"
female_25_male_28 = as.data.frame(rg_res$female_25_male_28)
  colnames(female_25_male_28) = "female_25_male_28"
female_28_male_18 = as.data.frame(rg_res$female_28_male_18)
  colnames(female_28_male_18) = "female_28_male_18"
female_28_male_25 = as.data.frame(rg_res$female_28_male_25)
  colnames(female_28_male_25) = "female_28_male_25"
female_28_male_28 = as.data.frame(rg_res$female_28_male_28)
  colnames(female_28_male_28) = "female_28_male_28"
male_18_male_25 = as.data.frame(rg_res$male_18_male_25)
  colnames(male_18_male_25) = "male_18_male_25"
male_18_male_28 = as.data.frame(rg_res$male_18_male_28)
  colnames(male_18_male_28) = "male_18_male_28"
male_25_male_28 = as.data.frame(rg_res$male_25_male_28)
  colnames(male_25_male_28) = "male_25_male_28"

all_rg <- cbind(female_18_female_25,
                female_18_female_28,
                female_18_male_18,
                female_18_male_25,
                female_18_male_28,
                female_25_female_28,
                female_25_male_18,
                female_25_male_25,
                female_25_male_28,
                female_28_male_18,
                female_28_male_25,
                female_28_male_28,
                male_18_male_25,
                male_18_male_28,
                male_25_male_28)

stack_all_rg <- stack(all_rg)

###Make All Boxplot
boxplot_all <- ggplot(stack_all_rg, aes(x=ind, y=values))+
                geom_boxplot()+
                labs(title = 'Complete Correlation Plot', x = 'Temperature and Sex Groups', y = 'Correlation Values')+
                theme(axis.text.x = element_text(angle = 30))+
                scale_y_continuous(limits=c(0,1))
boxplot_all
```

