---
title: Boxplot Results
date: “2022-02-28"
output:
  workflowr::wflow_html:
    toc: FALSE
    self_contained: no
    df_print: tibble
    theme: spacelab
    code_folding: show
    css: style.css

editor_options:
  chunk_output_type: console
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About
The boxplots below separated the data sets by sex and did univariate and multivariate analysis of the lifespans of the drosophila in three separate temperature conditions: 18C, 25C, and 28C. Within the plots the boxplots are grouped by temperature for univariate and multivariate analysis. The values of the boxplot consist of 50 observations of the R squared values. Within the boxplots the red diamond shows the mean of the R squared values and the blue line shows the mean of 50 observations of the heritability values. The Female heritability Plot is first followed by the Male heritability Plot. 

## Female and Male heritability Plots
```{r}
library(ggplot2)

###Reading in results
female_res <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_h2_female.rds")
male_res <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_h2_male.rds")

###Female r2 data loaded into one file, then seperated and made into data frames
female_r2 <- list(female_r2_gblup=female_res$r2_gblup_FEMALE, female_r2_mvgblup=female_res$r2_mvgblup_FEMALE)
female_r2_gblub <- female_r2$female_r2_gblup
female_r2_gblub <- as.data.frame(female_r2_gblub)
female_r2_mvgblub <- female_r2$female_r2_mvgblup
female_r2_mvgblub <- as.data.frame(female_r2_mvgblub)
female_r2_data <- merge(female_r2_gblub, female_r2_mvgblub, by = 0)
rownames(female_r2_data) <- female_r2_data[,1]
female_r2_data <- female_r2_data[,-1]
colnames(female_r2_data) <- c('Female_18c_uni','Female_25c_uni','Female_28c_uni','Female_18c_multi','Female_25c_multi','Female_28c_multi')
female_r2_data <- female_r2_data[, c(1,4,2,5,3,6)]


###Male r2 data loaded into one file, then seperated and made into data frames
male_r2 <- list(male_r2_gblup=male_res$r2_gblup_MALE, male_r2_mvgblup=male_res$r2_mvgblup_MALE)
male_r2_gblub <- male_r2$male_r2_gblup
male_r2_gblub <- as.data.frame(male_r2_gblub)
male_r2_mvgblub <- male_r2$male_r2_mvgblup
male_r2_mvgblub <- as.data.frame(male_r2_mvgblub)
male_r2_data <- merge(male_r2_gblub, male_r2_mvgblub, by = 0)
rownames(male_r2_data) <- male_r2_data[,1]
male_r2_data <- male_r2_data[,-1]
colnames(male_r2_data) <- c('Male_18c_uni','Male_25c_uni','Male_28c_uni','Male_18c_multi','Male_25c_multi','Male_28c_multi')
male_r2_data <- male_r2_data[, c(1,4,2,5,3,6)]


###Female h2 data loaded into one file, then seperated and made into data frames
female_h2 <- list(female_h2_gblup=female_res$h2_gblup_FEMALE, female_h2_mvgblup=female_res$h2_mvgblup_FEMALE)
female_h2_gblub <- female_h2$female_h2_gblup
female_h2_gblub <- as.data.frame(female_h2_gblub)
female_h2_mvgblub <- female_h2$female_h2_mvgblup
female_h2_mvgblub <- as.data.frame(female_h2_mvgblub)
female_h2_data <- merge(female_h2_gblub, female_h2_mvgblub, by = 0)
rownames(female_h2_data) <- female_h2_data[,1]
female_h2_data <- female_h2_data[,-1]
colnames(female_h2_data) <- c('Female_18c_uni','Female_25c_uni','Female_28c_uni','Female_18c_multi','Female_25c_multi','Female_28c_multi')
female_h2_data <- female_h2_data[, c(1,4,2,5,3,6)]



###Male h2 data loaded into one file, then seperated and made into data frames
male_h2 <- list(male_h2_gblup=male_res$h2_gblup_MALE, male_h2_mvgblup=male_res$h2_mvgblup_MALE)
male_h2_gblub <- male_h2$male_h2_gblup
male_h2_gblub <- as.data.frame(male_h2_gblub)
male_h2_mvgblub <- male_h2$male_h2_mvgblup
male_h2_mvgblub <- as.data.frame(male_h2_mvgblub)
male_h2_data <- merge(male_h2_gblub, male_h2_mvgblub, by = 0)
rownames(male_h2_data) <- male_h2_data[,1]
male_h2_data <- male_h2_data[,-1]
colnames(male_h2_data) <- c('Male_18c_uni','Male_25c_uni','Male_28c_uni','Male_18c_multi','Male_25c_multi','Male_28c_multi')
male_h2_data <- male_h2_data[, c(1,4,2,5,3,6)]


###Finding average of female r2 data
female_r2_means <- (colMeans(female_r2_data, na.rm = TRUE))

###Finding average of female h2 data
female_h2_means <- (colMeans(female_h2_data, na.rm = TRUE))

#Fixing female data for Boxplot
stacked_female_r2_gblub <- stack(female_r2_gblub)
vec <- rep("Univariate", 150)
stacked_female_r2_gblub$Analysis <- vec
stacked_female_r2_mvgblub <- stack(female_r2_mvgblub)
vecmv <- rep("Multiivariate", 150)
stacked_female_r2_mvgblub$Analysis <- vecmv

stacked_female_h2_gblub <- stack(female_h2_gblub)
vec <- rep("Univariate", 150)
stacked_female_h2_gblub$Analysis <- vec
stacked_female_h2_mvgblub <- stack(female_h2_mvgblub)
vecmv <- rep("Multiivariate", 150)
stacked_female_h2_mvgblub$Analysis <- vecmv

stacked_female_r2_data <- rbind(stacked_female_r2_gblub, stacked_female_r2_mvgblub)

stacked_female_h2_data <- rbind(stacked_female_h2_gblub, stacked_female_h2_mvgblub)


###Finding average of male r2 data
male_r2_means <- (colMeans(male_r2_data, na.rm = TRUE))

###Finding average of male h2 data
male_h2_means <- (colMeans(male_h2_data, na.rm = TRUE))

#Fixing male data for Boxplot
stacked_male_r2_gblub <- stack(male_r2_gblub)
vec <- rep("Univariate", 150)
stacked_male_r2_gblub$Analysis <- vec
stacked_male_r2_mvgblub <- stack(male_r2_mvgblub)
vecmv <- rep("Multiivariate", 150)
stacked_male_r2_mvgblub$Analysis <- vecmv

stacked_male_h2_gblub <- stack(male_h2_gblub)
vec <- rep("Univariate", 150)
stacked_male_h2_gblub$Analysis <- vec
stacked_male_h2_mvgblub <- stack(male_h2_mvgblub)
vecmv <- rep("Multiivariate", 150)
stacked_male_h2_mvgblub$Analysis <- vecmv

stacked_male_r2_data <- rbind(stacked_male_r2_gblub, stacked_male_r2_mvgblub)

stacked_male_h2_data <- rbind(stacked_male_h2_gblub, stacked_male_h2_mvgblub)



##Female Boxplot
boxplot_female <- ggplot(stacked_female_r2_data, aes(x=ind, y=values, fill = Analysis))+
  geom_boxplot()+
  labs(title = 'Female Heritability Plot', x = 'Temperature in Celcius', y = 'heritability')+
  stat_summary(fun=mean, colour="darkred", geom="point",
             shape=18, size=3, position = position_dodge2(width = 0.75,
                                                        preserve = "single"))+
  stat_summary(data = stacked_female_h2_data, fun = mean, colour="blue",  geom="point",
               shape="-", size=10, position = position_dodge2(width = 0.75,
                                                            preserve = "single"))
boxplot_female

##Male Boxplot
boxplot_male <- ggplot(stacked_male_r2_data, aes(x=ind, y=values, fill = Analysis))+
  geom_boxplot()+
  labs(title = 'Male Heritability Plot', x = 'Temperature in Celcius', y = 'heritability')+
  stat_summary(fun=mean, colour="darkred", geom="point",
               shape=18, size=3, position = position_dodge2(width = 0.75,
                                                            preserve = "single"))+
  stat_summary(data = stacked_male_h2_data, fun = mean, colour="blue",  geom="point",
               shape="-", size=10, position = position_dodge2(width = 0.75,
                                                                       preserve = "single"))
boxplot_male
```
## 18C, 25C, and 28C heritability Plots

The boxplots below separated the data sets by the temperature environments: 18C, 25C, and 28C, and did univariate and multivariate analysis of the lifespans of the drosophila of both sexes withing the temperature environments. Within the plots the boxplots are grouped by temperature for univariate and multivariate analysis. The values of the boxplot consist of 50 observations of the R squared values. Within the boxplots the red diamond shows the mean of the R squared values and the blue line shows the mean of 50 observations of the heritability values. The  plot for the environemnt 18C is first followed by the 25C heritability Plot and then the 28C heritability Plot. 


```{r}
library(ggplot2)

###Reading in results
temp18c_res <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_18c.rds")
temp25c_res <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_25c.rds")
temp28c_res <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_28c.rds")

###18c r2 data loaded into one file, then seperated and made into data frames
temp18c_r2 <- list(temp18c_r2_gblup=temp18c_res$r2_gblup_18c, temp18c_r2_mvgblup=temp18c_res$r2_mvgblup_18c)
temp18c_r2_gblub <- temp18c_r2$temp18c_r2_gblup
temp18c_r2_gblub <- as.data.frame(temp18c_r2_gblub)
temp18c_r2_mvgblub <- temp18c_r2$temp18c_r2_mvgblup
temp18c_r2_mvgblub <- as.data.frame(temp18c_r2_mvgblub)
temp18c_r2_data <- merge(temp18c_r2_gblub, temp18c_r2_mvgblub, by = 0)
rownames(temp18c_r2_data) <- temp18c_r2_data[,1]
temp18c_r2_data <- temp18c_r2_data[,-1]
colnames(temp18c_r2_data) <- c('Female_18c_uni','Female_18c_multi','Male_18c_uni','Male_18c_multi')


###25c r2 data loaded into one file, then seperated and made into data frames
temp25c_r2 <- list(temp25c_r2_gblup=temp25c_res$r2_gblup_25c, temp25c_r2_mvgblup=temp25c_res$r2_mvgblup_25c)
temp25c_r2_gblub <- temp25c_r2$temp25c_r2_gblup
temp25c_r2_gblub <- as.data.frame(temp25c_r2_gblub)
temp25c_r2_mvgblub <- temp25c_r2$temp25c_r2_mvgblup
temp25c_r2_mvgblub <- as.data.frame(temp25c_r2_mvgblub)
temp25c_r2_data <- merge(temp25c_r2_gblub, temp25c_r2_mvgblub, by = 0)
rownames(temp25c_r2_data) <- temp25c_r2_data[,1]
temp25c_r2_data <- temp25c_r2_data[,-1]
colnames(temp25c_r2_data) <- c('Female_25c_uni','Female_25c_multi','Male_25c_uni','Male_25c_multi')


###28c r2 data loaded into one file, then seperated and made into data frames
temp28c_r2 <- list(temp28c_r2_gblup=temp28c_res$r2_gblup_28c, temp28c_r2_mvgblup=temp28c_res$r2_mvgblup_28c)
temp28c_r2_gblub <- temp28c_r2$temp28c_r2_gblup
temp28c_r2_gblub <- as.data.frame(temp28c_r2_gblub)
temp28c_r2_mvgblub <- temp28c_r2$temp28c_r2_mvgblup
temp28c_r2_mvgblub <- as.data.frame(temp28c_r2_mvgblub)
temp28c_r2_data <- merge(temp28c_r2_gblub, temp28c_r2_mvgblub, by = 0)
rownames(temp28c_r2_data) <- temp28c_r2_data[,1]
temp28c_r2_data <- temp28c_r2_data[,-1]
colnames(temp28c_r2_data) <- c('Female_28c_uni','Female_28c_multi','Male_28c_uni','Male_28c_multi')


###h2 data being input and organized

###18c h2 data loaded into one file, then seperated and made into data frames
temp18c_h2 <- list(temp18c_h2_gblup=temp18c_res$h2_gblup_18c, temp18c_h2_mvgblup=temp18c_res$h2_mvgblup_18c)
temp18c_h2_gblub <- temp18c_h2$temp18c_h2_gblup
temp18c_h2_gblub <- as.data.frame(temp18c_h2_gblub)
temp18c_h2_mvgblub <- temp18c_h2$temp18c_h2_mvgblup
temp18c_h2_mvgblub <- as.data.frame(temp18c_h2_mvgblub)
temp18c_h2_data <- merge(temp18c_h2_gblub, temp18c_h2_mvgblub, by = 0)
rownames(temp18c_h2_data) <- temp18c_h2_data[,1]
temp18c_h2_data <- temp18c_h2_data[,-1]
colnames(temp18c_h2_data) <- c('Female_18c_uni','Female_18c_multi','Male_18c_uni','Male_18c_multi')

###25c h2 data loaded into one file, then seperated and made into data frames
temp25c_h2 <- list(temp25c_h2_gblup=temp25c_res$h2_gblup_25c, temp25c_h2_mvgblup=temp25c_res$h2_mvgblup_25c)
temp25c_h2_gblub <- temp25c_h2$temp25c_h2_gblup
temp25c_h2_gblub <- as.data.frame(temp25c_h2_gblub)
temp25c_h2_mvgblub <- temp25c_h2$temp25c_h2_mvgblup
temp25c_h2_mvgblub <- as.data.frame(temp25c_h2_mvgblub)
temp25c_h2_data <- merge(temp25c_h2_gblub, temp25c_h2_mvgblub, by = 0)
rownames(temp25c_h2_data) <- temp25c_h2_data[,1]
temp25c_h2_data <- temp25c_h2_data[,-1]
colnames(temp25c_h2_data) <- c('Female_18c_uni','Female_18c_multi','Male_18c_uni','Male_18c_multi')

###28c h2 data loaded into one file, then seperated and made into data frames
temp28c_h2 <- list(temp28c_h2_gblup=temp28c_res$h2_gblup_28c, temp28c_h2_mvgblup=temp28c_res$h2_mvgblup_28c)
temp28c_h2_gblub <- temp28c_h2$temp28c_h2_gblup
temp28c_h2_gblub <- as.data.frame(temp28c_h2_gblub)
temp28c_h2_mvgblub <- temp28c_h2$temp28c_h2_mvgblup
temp28c_h2_mvgblub <- as.data.frame(temp28c_h2_mvgblub)
temp28c_h2_data <- merge(temp28c_h2_gblub, temp28c_h2_mvgblub, by = 0)
rownames(temp28c_h2_data) <- temp28c_h2_data[,1]
temp28c_h2_data <- temp28c_h2_data[,-1]
colnames(temp28c_h2_data) <- c('Female_18c_uni','Female_18c_multi','Male_18c_uni','Male_18c_multi')


###Finding average of 18c r2 data
temp18c_r2_means <- (colMeans(temp18c_r2_data, na.rm = TRUE))

###Finding average of 18c h2 data
temp18c_h2_means <- (colMeans(temp18c_h2_data, na.rm = TRUE))

#Fixing 18C data for Boxplot
stacked_temp18c_r2_gblub <- stack(temp18c_r2_gblub)
vec <- rep("Univariate", 100)
stacked_temp18c_r2_gblub$Analysis <- vec
stacked_temp18c_r2_mvgblub <- stack(temp18c_r2_mvgblub)
vecmv <- rep("Multiivariate", 100)
stacked_temp18c_r2_mvgblub$Analysis <- vecmv

stacked_temp18c_h2_gblub <- stack(temp18c_h2_gblub)
vec <- rep("Univariate", 100)
stacked_temp18c_h2_gblub$Analysis <- vec
stacked_temp18c_h2_mvgblub <- stack(temp18c_h2_mvgblub)
vecmv <- rep("Multiivariate", 100)
stacked_temp18c_h2_mvgblub$Analysis <- vecmv

stacked_temp18c_r2_data <- rbind(stacked_temp18c_r2_gblub, stacked_temp18c_r2_mvgblub)

stacked_temp18c_h2_data <- rbind(stacked_temp18c_h2_gblub, stacked_temp18c_h2_mvgblub)


###Finding average of 25c r2 data
temp25c_r2_means <- (colMeans(temp25c_r2_data, na.rm = TRUE))

###Finding average of 25c h2 data
temp25c_h2_means <- (colMeans(temp25c_h2_data, na.rm = TRUE))

#Fixing 25C data for Boxplot
stacked_temp25c_r2_gblub <- stack(temp25c_r2_gblub)
vec <- rep("Univariate", 100)
stacked_temp25c_r2_gblub$Analysis <- vec
stacked_temp25c_r2_mvgblub <- stack(temp25c_r2_mvgblub)
vecmv <- rep("Multiivariate", 100)
stacked_temp25c_r2_mvgblub$Analysis <- vecmv

stacked_temp25c_h2_gblub <- stack(temp25c_h2_gblub)
vec <- rep("Univariate", 100)
stacked_temp25c_h2_gblub$Analysis <- vec
stacked_temp25c_h2_mvgblub <- stack(temp25c_h2_mvgblub)
vecmv <- rep("Multiivariate", 100)
stacked_temp25c_h2_mvgblub$Analysis <- vecmv

stacked_temp25c_r2_data <- rbind(stacked_temp25c_r2_gblub, stacked_temp25c_r2_mvgblub)

stacked_temp25c_h2_data <- rbind(stacked_temp25c_h2_gblub, stacked_temp25c_h2_mvgblub)


###Finding average of 28c r2 data
temp28c_r2_means <- (colMeans(temp28c_r2_data, na.rm = TRUE))

###Finding average of 28c h2 data
temp28c_h2_means <- (colMeans(temp28c_h2_data, na.rm = TRUE))

#Fixing 28C data for Boxplot
stacked_temp28c_r2_gblub <- stack(temp28c_r2_gblub)
vec <- rep("Univariate", 100)
stacked_temp28c_r2_gblub$Analysis <- vec
stacked_temp28c_r2_mvgblub <- stack(temp28c_r2_mvgblub)
vecmv <- rep("Multiivariate", 100)
stacked_temp28c_r2_mvgblub$Analysis <- vecmv

stacked_temp28c_h2_gblub <- stack(temp28c_h2_gblub)
vec <- rep("Univariate", 100)
stacked_temp28c_h2_gblub$Analysis <- vec
stacked_temp28c_h2_mvgblub <- stack(temp28c_h2_mvgblub)
vecmv <- rep("Multiivariate", 100)
stacked_temp28c_h2_mvgblub$Analysis <- vecmv

stacked_temp28c_r2_data <- rbind(stacked_temp28c_r2_gblub, stacked_temp28c_r2_mvgblub)

stacked_temp28c_h2_data <- rbind(stacked_temp28c_h2_gblub, stacked_temp28c_h2_mvgblub)



##18C Boxplot
boxplot_18c <- ggplot(stacked_temp18c_r2_data, aes(x=ind, y=values, fill = Analysis))+
  geom_boxplot()+
  labs(title = '18C Heritability Plot', x = 'Temperature in Celcius', y = 'heritability')+
  stat_summary(fun=mean, colour="darkred", geom="point",
               shape=18, size=3, position = position_dodge2(width = 0.75,
                                                            preserve = "single"))+
  stat_summary(data = stacked_temp18c_h2_data, fun = mean, colour="blue",  geom="point",
               shape="-", size=10, position = position_dodge2(width = 0.75,
                                                                       preserve = "single"))
boxplot_18c

##25C Boxplot
boxplot_25c <- ggplot(stacked_temp25c_r2_data, aes(x=ind, y=values, fill = Analysis))+
  geom_boxplot()+
  labs(title = '25C Heritability Plot', x = 'Temperature in Celcius', y = 'heritability')+
  stat_summary(fun=mean, colour="darkred", geom="point",
               shape=18, size=3, position = position_dodge2(width = 0.75,
                                                            preserve = "single"))+
  stat_summary(data = stacked_temp25c_h2_data, fun = mean, colour="blue",  geom="point",
               shape="-", size=10, position = position_dodge2(width = 0.75,
                                                                       preserve = "single"))

boxplot_25c

##28C Boxplot
boxplot_28c <- ggplot(stacked_temp28c_r2_data, aes(x=ind, y=values, fill = Analysis))+
  geom_boxplot()+
  labs(title = '28C Heritability Plot', x = 'Temperature in Celcius', y = 'heritability')+
  stat_summary(fun=mean, colour="darkred", geom="point",
               shape=18, size=3, position = position_dodge2(width = 0.75,
                                                            preserve = "single"))+
  stat_summary(data = stacked_temp28c_h2_data, fun = mean, colour="blue",  geom="point",
               shape="-", size=10, position = position_dodge2(width = 0.75,
                                                                       preserve = "single"))
boxplot_28c

```

## Full Data Analysis

The boxplots below took all the available data for the lifespan of drosophila and performed univariate and multivariate analysis. The values of the boxplot consist of 50 observations of the R squared values. Within the boxplots the red diamond shows the mean of the R squared values and the blue line shows the mean of 50 observations of the heritability values.
```{r}
library(ggplot2)

###Reading in results
all_res <- readRDS("/data/morgante_lab/kcoyne/mv_project/results/gblup_vs_mvgblup_drosophila_all.rds")

###r2 data loaded into one file, then seperated and made into data frames
all_r2 <- list(r2_gblup=all_res$r2_gblup, r2_mvgblup=all_res$r2_mvgblup)
r2_gblub <- all_r2$r2_gblup
r2_gblub <- as.data.frame(r2_gblub)
r2_mvgblub <- all_r2$r2_mvgblup
r2_mvgblub <- as.data.frame(r2_mvgblub)
r2_data <- merge(r2_gblub, r2_mvgblub, by = 0)
rownames(r2_data) <- r2_data[,1]
r2_data <- r2_data[,-1]
r2_data <- r2_data[, c(1,7,2,8,3,9,4,10,5,11,6,12)]
colnames(r2_data) <- c('Female_18c_uni','Female_18c_multi','Female_25c_uni','Female_25c_multi','Female_28c_uni','Female_28c_multi','Male_18c_uni','Male_18c_multi','Male_25c_uni','Male_25c_multi','Male_28c_uni','Male_28c_multi')


###h2 data loaded into one file, then seperated and made into data frames
all_h2 <- list(h2_gblup=all_res$h2_gblup, h2_mvgblup=all_res$h2_mvgblup)
h2_gblub <- all_h2$h2_gblup
h2_gblub <- as.data.frame(h2_gblub)
h2_mvgblub <- all_h2$h2_mvgblup
h2_mvgblub <- as.data.frame(h2_mvgblub)
h2_data <- merge(h2_gblub, h2_mvgblub, by = 0)
rownames(h2_data) <- h2_data[,1]
h2_data <- h2_data[,-1]
h2_data <- h2_data[, c(1,7,2,8,3,9,4,10,5,11,6,12)]
colnames(h2_data) <- c('Female_18c_uni','Female_18c_multi','Female_25c_uni','Female_25c_multi','Female_28c_uni','Female_28c_multi','Male_18c_uni','Male_18c_multi','Male_25c_uni','Male_25c_multi','Male_28c_uni','Male_28c_multi')


###Finding average of r2 data
r2_means <- (colMeans(r2_data, na.rm = TRUE))

###Finding average of h2 data
h2_means <- (colMeans(h2_data, na.rm = TRUE))

#Fixing data for Boxplot
stacked_r2_gblub <- stack(r2_gblub)
vec <- rep("Univariate", 100)
stacked_r2_gblub$Analysis <- vec
stacked_r2_mvgblub <- stack(r2_mvgblub)
vecmv <- rep("Multiivariate", 100)
stacked_r2_mvgblub$Analysis <- vecmv

stacked_h2_gblub <- stack(h2_gblub)
vec <- rep("Univariate", 100)
stacked_h2_gblub$Analysis <- vec
stacked_h2_mvgblub <- stack(h2_mvgblub)
vecmv <- rep("Multiivariate", 100)
stacked_h2_mvgblub$Analysis <- vecmv

stacked_r2_data <- rbind(stacked_r2_gblub, stacked_r2_mvgblub)

stacked_h2_data <- rbind(stacked_h2_gblub, stacked_h2_mvgblub)


##Boxplot
boxplot <- ggplot(stacked_r2_data, aes(x=ind, y=values, fill = Analysis))+
  geom_boxplot()+
  labs(title = 'Heritability Plot', x = 'Temperature and Sex Groups', y = 'heritability')+
  stat_summary(fun=mean, colour="darkred", geom="point",
               shape=18, size=3, position = position_dodge2(width = 0.75,
                                                            preserve = "single"))+
  stat_summary(data = stacked_h2_data, fun = mean, colour="blue",  geom="point",
               shape="-", size=10, position = position_dodge2(width = 0.75,
                                                              preserve = "single"))
boxplot
```

